map

### 2022-03-01 data analysis/map.Rmd
as

```{r}
#  US National Atlas Equal Area projection (CRS 2163)
usa <- subset(world, admin == "United States of America")
(mainland <- ggplot(data = usa) +
    geom_sf(fill = "cornsilk") +
    geom_sf(data = sites, size = 2, shape = c(15, 16, 17, 18, 19)) +
    coord_sf(crs = st_crs(2163), xlim = c(-2500000, 2500000), ylim = c(-2300000, 
         730000)))
```

@@

ggsave("figures/map.png", width = 7, heigh = 4)
```

>>>>

```{r}
#  US National Atlas Equal Area projection (CRS 2163)
usa <- subset(world, admin == "United States of America")
(mainland <- ggplot(data = usa) +
    geom_sf(fill = "cornsilk") +
    geom_sf(data = sites, size = 2, shape = 16) +
    coord_sf(crs = st_crs(2163), xlim = c(-2500000, 2500000), ylim = c(-2300000, 
         730000)))
```

@@

ggsave("figures/Figure 1.png", width = 7, heigh = 4)
```
